\huge Tor's Usability for Censorship Circumvention

### 2016-04-11 pets2017-paper/pets2017-paper.tex
restructure redesign section

\begin{enumerate}
    \item  {\bfseries Visibility of system status}: provide feedback on what the system is doing.
    \item  {\bfseries User control and freedom}: allow users to override system, supports undo and redo actions. 
    \item  {\bfseries Error management}: expressing errors in plain language and offering a solution. 
    \item  {\bfseries Understandable language}: explaining the task, rather than technical concepts. 
    \item  {\bfseries Simple design}: showing options on an as-needed basis. 
\end{enumerate}

@@

Tor Browser 5.0.3. configuration interface does not adequately meet our heuristic evaluation criteria from Section~\ref{sec:goals}: visibility of system status, user control and freedom, error management, understandable language, and minimal design. The configuration used for a connection is not visible to the users before they connect or while they are connecting. Users had full control but little guidance. Error messages do not express errors in plain language nor offer solutions. The text was too technical for an average user to understand. The interface can be simplified visually.

Our goals in redesigning the interface was to making the system status visible to the user, retain user freedom but give guidance, make the vocabulary more accessible, offer solutions upon errors, and to require the user to make fewer decisions overall. To achieve these goals, we made the following changes: \\

@@

\begin{enumerate} \itemsep1pt \parskip0pt \parsep0pt 
\item {\bfseries Added system status visibility.} Before any attempt to connect to the Tor network, a summary screen displays if a bridge or proxy is configured, and if so, what the configurations are. The progress screen also displays the configurations while the connection attempt is being made. 
\item {\bfseries Added guidance on choosing connect vs configure.} We labeled the configure option as advanced, manual, and only for heavily censored situations. 
\item {\bfseries Got rid of proxy and bridge questions.}  We removed the bridge and proxy questions, which were highly technical and challenging for users to answer. There are two less screens in the interface.
\item {\bfseries Added auto-detect for proxies.} Auto-detection of proxies can be done locally, by scanning system files. This is safe even for at-risk users, and greatly simplifies the configuration process. 
\item {\bfseries Switched ordering to configure proxies first.} To build up the users' mental model, we configure network components in a topologically sequential. Previously, proxies were put after bridge configuration because only a small fraction of users require proxies. With auto-detection, configuring a proxy before a bridge will not burden the users. 
\item {\bfseries Added explicit advice on choosing bridges.} The default bridge is still obfs3. There is added text that advises users to try a meek bridge if obfs3 does not work. This advice is tailored for our participants who were in the advanced censorship environment. 
\item {\bfseries Added clear feedback to the progress bar.} We switched the continuous progress bar to a discrete checkpoint based progress bat that network components involved in connecting to the Tor network. This aligns with the metal model we are trying to build. As connections are made with components, the progress bar displays a green check, giving immediate feedback to the user. For instance, a user can can now see that the bridge was configured correctly, and they just need to wait to connect to the Tor network. Upon failure, users can see which components that have succeeded and which have failed.
\item {\bfseries Added instructions on what to try next on errors.} When an error occurs, text advice on what to try next is shown to the user. Such advice includes trying the connection again, choosing a different bridge, or trying a connection without a proxy. 
\item {\bfseries Reduced overall amount of text and made text less technical.} We make the text more task-centric by focusing on instructing users through the configuration process, at the sacrifice of explaining technical concepts to users. Since users generally couldn't understand the technical concepts enough to influence their decisions, giving direct guidance may be a better option.  
\item {\bfseries Reduced visual clutter.} We showed options on an as-needed basis and we minimized the amount of text on the screen. For instance, additional fields were hidden until the relevant options were chosen. Additional stylistic simplifications were made, such as removing grouping boxes. 
\end{enumerate}

>>>>

\begin{enumerate}
    \item  {\bfseries Visibility of system status}: provide feedback on what the system is doing. 
    \item  {\bfseries Error management}: expressing errors in plain language and offering a solution. 
    \item  {\bfseries Understandable language}: explaining the task, rather than technical concepts. 
    \item  {\bfseries Simple design}: showing options on an as-needed basis. 
\end{enumerate}

@@

Tor Browser 5.0.3. configuration interface does not adequately meet our heuristic evaluation criteria from Section~\ref{sec:goals}: visibility of system status, user control and freedom, error management, understandable language, and minimal design. We rate the severity of the issue by its frequency, impact, and persistence ~\cite{nielsen1994heuristic}:\\

\begin{enumerate}
\item {\bfseries Major Problem}: Error messages do not express errors in plain language nor offer solutions. 
\item {\bfseries Major Problem}: The text was too technical for an average user to understand. 
\item {\bfseries Minor Problem}: The configuration is not visible to the users before they connect or while they are connecting.
\item {\bfseries Cosmetic Problem}: The interface can be simplified visually.  
 \end{enumerate}

To fix the aforementioned problems, we made the following changes: \\

@@

\begin{enumerate}
\item {\bfseries Added instructions on what to try next on errors.} When an error occurs, text advice on what to try next is shown to the user. Such advice includes trying the connection again, choosing a different bridge, or trying a connection without a proxy. 
\item {\bfseries Reduced overall amount of text and made text less technical.} We make the text more task-centric by focusing on instructing users through the configuration process, at the sacrifice of explaining technical concepts to users. Since users generally couldn't understand the technical concepts enough to influence their decisions, giving direct guidance may be a better option. 
\item {\bfseries Added system status visibility.} Before any attempt to connect to the Tor network, a summary screen displays if a bridge or proxy is configured, and if so, what the configurations are. The progress screen also displays the configurations while the connection attempt is being made. 
\item {\bfseries Reduced visual clutter.} We showed options on an as-needed basis and we minimized the amount of text on the screen. For instance, additional fields were hidden until the relevant options were chosen. Additional stylistic simplifications were made, such as removing grouping boxes. 
\end{enumerate}

We also made additional changes to unburden the user (5-8) and build a mental model (9-10):\\

\begin{enumerate}
\setcounter{enumi}{4}
\item {\bfseries Added guidance on choosing connect vs configure.} We labeled the configure option as advanced, manual, and only for heavily censored situations. 
\item {\bfseries Got rid of proxy and bridge questions.}  We removed the bridge and proxy questions, which were highly technical and challenging for users to answer. There are two less screens in the interface.
\item {\bfseries Added auto-detect for proxies.} Auto-detection of proxies can be done locally, by scanning system files. This is safe even for at-risk users, and greatly simplifies the configuration process. 
\item {\bfseries Added explicit advice on choosing bridges.} The default bridge is still obfs3. There is added text that advises users to try a meek bridge if obfs3 does not work. This advice is tailored for our participants who were in the advanced censorship environment.

\item {\bfseries Switched ordering to configure proxies first.} To build up the users' mental model, we configure network components in a topologically sequential. Previously, proxies were put after bridge configuration because only a small fraction of users require proxies. With auto-detection, configuring a proxy before a bridge will not burden the users. 
\item {\bfseries Added clear feedback to the progress bar.} We switched the continuous progress bar to a discrete checkpoint based progress bat that network components involved in connecting to the Tor network. This aligns with the metal model we are trying to build. As connections are made with components, the progress bar displays a green check, giving immediate feedback to the user. For instance, a user can can now see that the bridge was configured correctly, and they just need to wait to connect to the Tor network. Upon failure, users can see which components that have succeeded and which have failed.
\end{enumerate}
